Analysis

### 2022-02-02 code/R/Analysis.Rmd
Added figures and tables. Added examples of annotated images.

@@

thul01 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(id_gt)), size = 1, shape = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("THUL-01 Ground Truth") +
  theme(legend.position = "none")
```

>>>>

# Camera codes:
# 2018 NARS-04: 2018 NARS A
# 2018 THUL-01: 2018 THUL B
# 2019 NARS-13: 2019 NARS C
# 2019 NARS-17: 2019 NARS D
# 2019 NYAA-04: 2019 NYAA E

all = all %>% 
  mutate("camCode" = case_when(CameraID == "THUL-01"~ "2018 THUL B", CameraID == "NARS-04"~ "2018 NARS A", CameraID == "NARS-13"~ "2019 NARS C", CameraID == "NARS-17"~ "2019 NARS D", CameraID == "NYALE-04"~ "2019 NYAA E"))

axisSize = 30
legendTitleSize = 30
legendTextSize = 28

f1 = all %>% 
ggplot()+
  geom_point(aes(x = flower_start, y = flower_length, fill = camCode, shape = camCode), size = 8) + 
  xlab("Onset of flowering (DOY)") + 
  ylab("Number of days flowering") +
    theme_bw()  +
  scale_fill_manual(name = "Camera ID",
                      values = c("gray26", "brown3", "dodgerblue3", "darkorange2", "chartreuse3"), aesthetics = c("colour", "fill")) + 
  scale_shape_manual(name = "Camera ID",
                      values = c(21,22,23,24,25)) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.title = element_text(size = legendTitleSize),
        text = element_text(size = axisSize),
        legend.text = element_text(size = legendTextSize),
        axis.line = element_line(),
        axis.text=element_text(colour="black"),
        panel.spacing = unit(0.7, "lines"))

f1

ggsave("U:/BITCue/Projekter/TrackingFlowers/figures/OnsetVSLength.png", f1, width = 15, height = 10)

@@

thul01 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(Class)), size = 1, shape = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("THUL-01 Ground Truth") +
  theme(legend.position = "none")
```
